DATA 624 Project 1 Part A - ATM

### 2020-03-23 DATA624/Project 1-A ATM.Rmd
More work on Project 1

>>>>

This model is quite different from the two proceeding cases.  You can see it in the plot:

```{r}
atm %>%
  filter(ATM == "ATM3") %>%
  mutate(nonzero = if_else(Cash == 0, "No", "Yes")) %>%
  ggplot(aes(DATE, Cash, color=nonzero)) +
  geom_point() +
  ggtitle("ATM #3") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.title = element_blank(), legend.position = "none")
```

Most of the values are zeros (points in red above), except for 3 points (shown in blue).  The three non-zero points are the most current.

## ATM #4

This ATM is different too, but not as radically different as ATM #3.  I will be using the same approach used for ATM #1 and #2 with this ATM.

There is one major outlier in the data set.  We will clean it up by simply by using the `tsclean` function once again.

```{r}
atm4 <- atm %>%
  filter(ATM == "ATM4")

atm4$clean_cash <- c(tsclean(ts(atm4$Cash, start = decimal_date(as.Date(min(atm4$DATE))), frequency = 365)))

atm4_ts <- ts(atm4$clean_cash, start = decimal_date(as.Date(min(atm4$DATE))), frequency = 7)
ggtsplot(atm4_ts, "ATM #4")
```

Once again there is the familiar patter of peaks on the multiples of seven.

```{r}
atm4_stl_ets_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="ets")
checkresiduals(atm4_stl_ets_fit)
```

This model did a fair job.  There are a couple of ACF spikes that are outside the bands.  Let's see if the ARIMA model does better:

```{r}
atm4_stl_arima_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="arima") 
checkresiduals(atm4_stl_arima_fit)
```

This is an improvement over the STL+ETS model.  There are still a couple of spikes on the ACF that falls outside the threshold.

```{r}
atm4_hw_fit <- hw(atm4_ts, h = h)
checkresiduals(atm4_hw_fit)
```

This method seems to have preformed better than any of the STL models.

```{r}
atm4_lambda <- BoxCox.lambda(atm4_ts)
atm4_adj_hw_fit <- hw(atm4_ts, h = h, lambda = atm4_lambda)
checkresiduals(atm4_adj_hw_fit)
```

This model preformed very well.  It doesn't look like any of the ACF spikes are outside the bands.  This is a contender for sure.

```{r}
atm4_arima_fit <- auto.arima(atm4_ts)
checkresiduals(atm4_arima_fit)
```

This model did fairly well, but it seems like the Holt-Winters with Box-Cox adjustment did better.  It's time to cross-validate and see how all of them preform.

Once again, I will use the `tsCV` function and evaluate the models.  My goal to minimize the RMSE remains for this dataset.

```{r}
atm4_arima_forecast <- function(x, h) {
  forecast(Arima(x, order = c(0, 0, 3), seasonal = c(1, 0, 0)), h = h)
}

stl_ets_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method="ets")
stl_arima_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method="arima")
hw_errors <- tsCV(atm4_ts, hw, h = h)
adj_hw_errors <- tsCV(atm4_ts, hw, h = h, lambda = atm4_lambda)
arima_errors <- tsCV(atm4_ts, atm4_arima_forecast, h = h)

That's an unexpected result.  The Adjusted Holt-Winters (the one I thought would preform the best), did not preform as well.  The ARIMA model, once again, rose to the top.

Once again I will use the forecasts produced by the ARIMA model as the projections for ATM #4.
